---
title             : "Research Article"
shorttitle        : "Research Article"

author: 
  - name          : "My name"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Experimental Psychology, Ewert Place, Banbury road, Summertown, Oxford, OX2 7DD"
    email         : "my_email@psy.ox.ac.uk"
  - name          : "A.N.Other-Researcher"
    affiliation   : "1"
  - name          : "Dorothy V. M. Bishop"
    affiliation   : "1"


affiliation:
  - id            : "1"
    institution   : "Department of Experimental Psychology, University of Oxford"


abstract: >
  This is the abstract of my new paper. please update the text!
  
keywords          : "keyword1, keyword2, keyword3"
wordcount         : "X"

bibliography      : ["mybibfile.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
fig_caption       : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_word
---

```{r include = FALSE}
library("papaja")
```

  [@R-base]Here is the article text. Specifically, here is an equation,

$$LI=  \frac{(L-R)}{(L+R)}$$
   

## Section header
  blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah 
  
  blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah 

### *subsetion header*

   blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah 
  
  blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah 

Here is a link to DOI: [link](https://osf.io/t24rv/). 
  
 

## another new section

You can include R plots or tables at the end like this.

```{r, fig.width=11, fig.height=8, message=FALSE, warning=FALSE, fig.cap='Forest plot...'}

hist(rnorm(1000,0,1))

```


## Funding

  This work was supported by ...

## Acknowledgements

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}


